\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-06 paper.qmd
Updated benchmark value of 2nd figure 9

```{r}
#| label: hexbin-regular-two-curvy2
## hexagon binning to have regular hexagons
hb_obj_two_curvy2 <- hex_binning(
  data = tsne_two_curvy_scaled, 
  bin1 = 13, 
  r2 = r2)

a1_2 <- calc_bins_y(
  bin1 = 13, 
  r2 = r2
  )$a1

@@

benchmark_two_curvy <- 3.5 * bin_width

@@

two_curvy_proj_umap_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("c2", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )

@@

```{r}
#| label: fig-rm-lg
#| fig-cap: "Distribution of edge lengths and wireframes in \\gD{} and $7\\text{-}D$ with Delaunay triangulation, and two choices of long edge removal: (b) benchmark = 4.5$a_1$ and (c) benchmark = 2$a_1$, where $a_1$ = 0.09."
#| fig-height: 15
#| fig-width: 15

>>>>

```{r}
#| label: hexbin-regular-two-curvy2
## hexagon binning to have regular hexagons
hb_obj_two_curvy2 <- hex_binning(
  data = tsne_two_curvy_scaled, 
  bin1 = 23, 
  r2 = r2)

a1_2 <- calc_bins_y(
  bin1 = 23, 
  r2 = r2
  )$a1

@@

benchmark_two_curvy <- 2.5 * bin_width

@@

two_curvy_proj_umap_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.1, 0.1)) + 
  ylim(c(-0.1, 0.1)) +
  interior_annotation("c2", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )

@@

```{r}
#| label: fig-rm-lg
#| fig-cap: "Distribution of edge lengths and wireframes in \\gD{} and $7\\text{-}D$ with Delaunay triangulation, and two choices of long edge removal: (b) benchmark = 2.5$a_1$ and (c) benchmark = 2$a_1$, where $a_1$ = 0.09."
#| fig-height: 15
#| fig-width: 15

### 2025-01-06 paper.tex
Updated Figure 7
Updated benchmark value of 2nd figure 9

\caption{\label{fig-bins-two-curvy}Hexbin density plots of UMAP layout
of the two C-shaped clusters data, using three different bin inputs: (a)
\(b = 80 \text{ } (10, \text{ }8)\), (b)
\(b = 130 \text{ } (13, \text{ }10)\), and (c)
\(b = 391 \text{ } (23, \text{ }17)\). Color indicates standardized
counts, dark indicating high count and light indicates low count. At the
smallest bin size, the data structure is discontinuous, suggesting that
there are too many bins. Using the MSE of the model fit in
\(7\text{-}D\) helps decide on a useful choice of number of bins.}

@@

\caption{\label{fig-rm-lg}Distribution of edge lengths and wireframes in
\gD{} and \(7\text{-}D\) with Delaunay triangulation, and two choices of
long edge removal: (b) benchmark = 4.5\(a_1\) and (c) benchmark =
2\(a_1\), where \(a_1\) = 0.09.}

>>>>

\caption{\label{fig-bins-two-curvy}Hexbin density plots of tSNE layout
of the two C-shaped clusters data, using three different bin inputs: (a)
\(b = 80 \text{ } (10, \text{ }8)\), (b)
\(b = 130 \text{ } (13, \text{ }10)\), and (c)
\(b = 391 \text{ } (23, \text{ }17)\). Color indicates standardized
counts, dark indicating high count and light indicates low count. At the
smallest bin size, the data structure is discontinuous, suggesting that
there are too many bins. Using the MSE of the model fit in
\(7\text{-}D\) helps decide on a useful choice of number of bins.}

@@

\caption{\label{fig-rm-lg}Distribution of edge lengths and wireframes in
\gD{} and \(7\text{-}D\) with Delaunay triangulation, and two choices of
long edge removal: (b) benchmark = 2.5\(a_1\) and (c) benchmark =
2\(a_1\), where \(a_1\) = 0.09.}
